Psychological Needs During Intergroup Contact

### 2021-12-16 Tables/mdlContactGeneral.tex
linebreaks

\hspace{1em}$\tau_{11}$ &  &  &  &  &  &  &  &  & 48.94 (PID.OutgroupInteraction)\n 7.23 (PID.NonOutgroupInteraction) &  & 40.53 (PID.OutgroupInteraction)\n 3.43 (PID.NonOutgroupInteraction) & \\
\hspace{1em}$\rho_{01}$ &  &  &  &  &  &  &  &  & -0.72 (PID.OutgroupInteraction)\n 0.12 (PID.NonOutgroupInteraction) &  & -0.70 (PID.OutgroupInteraction)\n-0.28 (PID.NonOutgroupInteraction) & \\

@@

\multicolumn{13}{l}{\rule{0pt}{1em}\$\textbackslash{}sigma\textasciicircum{}2\$: residual variance, \$\textbackslash{}tau\_\{00\}\$: random intercept variance, \$\textbackslash{}tau\_\{11\}\$: random slope variance(s), \$\textbackslash{}rho\_\{01\}\$: random slope-intercept correlation(s) , \$\textbackslash{}rho\_\{00\}\$: correlation(s) between random slopes}\\
\multicolumn{13}{l}{\rule{0pt}{1em}**** \$p\$ < .0001, *** \$p\$ < .001, ** \$p\$ < .01, * \$p\$ < .05}\\
\multicolumn{13}{l}{\rule{0pt}{1em}\textsuperscript{a} For linear regression: \$R\textasciicircum{}2 / R\textasciicircum{}2\_\{adjusted\}\$, for multilevel regression: \$R\textasciicircum{}2\_\{marginal\} / R\textasciicircum{}2\_\{conditional\}\$ }\\

>>>>

\hspace{1em}$\tau_{11}$ &  &  &  &  &  &  &  &  & \makecell[r]{48.94 (PID.OutgroupInteraction)\\ 7.23 (PID.NonOutgroupInteraction)} &  & \makecell[r]{40.53 (PID.OutgroupInteraction)\\ 3.43 (PID.NonOutgroupInteraction)} & \\
\hspace{1em}$\rho_{01}$ &  &  &  &  &  &  &  &  & \makecell[l]{-0.72 (PID.OutgroupInteraction)\\ 0.12 (PID.NonOutgroupInteraction)} &  & \makecell[l]{-0.70 (PID.OutgroupInteraction)\\-0.28 (PID.NonOutgroupInteraction)} & \\

@@

\multicolumn{13}{l}{\rule{0pt}{1em}$sigma^2$: residual variance, $tau_{00}$: random intercept variance, $tau_{11}$: random slope variance(s), $rho_{01}$: random slope-intercept correlation(s) , $rho_{00}$: correlation(s) between random slopes}\\
\multicolumn{13}{l}{\rule{0pt}{1em}**** $p$ < .0001, *** $p$ < .001, ** $p$ < .01, * $p$ < .05}\\
\multicolumn{13}{l}{\rule{0pt}{1em}\textsuperscript{a} For linear regression: $R^2 / R^2_{adjusted}$, for multilevel regression: $R^2_{marginal} / R^2_{conditional}$ }\\

### 2021-12-16 Tables/mdlRobustness.tex
linebreaks

\hspace{1em}$\tau_{11}$ & 0.01 (PID.CoreNeed)\n6.05 (PID.OutgroupInteraction) &  & 0.00 (PID.CoreNeed)\n46.82 (PID.OutgroupInteraction) &  & 0.01 (PID.CoreNeed)\n40.96 (PID.OutgroupInteraction) &  & 0.02 (PID.CoreNeed)\n0.20 (PID.Competence)\n0.14 (PID.Autonomy)\n0.00 (PID.Relatedness) &  & 0.01 (PID.CoreNeed)\n0.00 (PID.Competence)\n0.00 (PID.Autonomy)\n0.00 (PID.Relatedness) &  & 0.05 (PID.CoreNeed)\n0.01 (PID.Competence)\n0.00 (PID.Autonomy)\n0.01 (PID.Relatedness) & \\
\hspace{1em}$\rho_{01}$ & 0.01 (PID.CoreNeed)\n-0.27 (PID.OutgroupInteraction) &  & 0.27 (PID.CoreNeed)\n-0.68 (PID.OutgroupInteraction) &  & -0.15 (PID.CoreNeed)\n-0.68 (PID.OutgroupInteraction) &  & 0.55 (PID.CoreNeed)\n-0.15 (PID.Competence)\n-0.09 (PID.Autonomy)\n 0.56 (PID.Relatedness) &  & -0.16 (PID.CoreNeed)\n-0.05 (PID.Competence)\n-0.44 (PID.Autonomy)\n-0.20 (PID.Relatedness) &  & -0.25 (PID.CoreNeed)\n-0.29 (PID.Competence)\n-0.23 (PID.Autonomy)\n 0.02 (PID.Relatedness) & \\
\hspace{1em}$\rho_{00}$ & 0.33 (PID.CoreNeed-OutgroupInteraction) &  & -0.08 (PID.CoreNeed-OutgroupInteraction) &  & 0.01 (PID.CoreNeed-OutgroupInteraction) &  & 0.03 (PID.CoreNeed-Autonomy)\n-0.93 (PID.Competence-Autonomy)\n-0.11 (PID.CoreNeed-Competence)\n 0.17 (PID.CoreNeed-Relatedness)\n 0.16 (PID.Competence-Relatedness)\n-0.10 (PID.Autonomy-Relatedness) &  & 0.60 (PID.CoreNeed-Autonomy)\n 0.83 (PID.Competence-Autonomy)\n 0.20 (PID.CoreNeed-Competence)\n 0.42 (PID.CoreNeed-Relatedness)\n-0.79 (PID.Competence-Relatedness)\n-0.35 (PID.Autonomy-Relatedness) &  & 0.57 (PID.CoreNeed-Autonomy)\n-0.68 (PID.Competence-Autonomy)\n 0.09 (PID.CoreNeed-Competence)\n-0.27 (PID.CoreNeed-Relatedness)\n-0.31 (PID.Competence-Relatedness)\n-0.08 (PID.Autonomy-Relatedness) & \\

>>>>

\hspace{1em}$\tau_{11}$ & \makecell[l]{0.01 (PID.CoreNeed)\\6.05 (PID.OutgroupInteraction)} &  & \makecell[l]{ 0.00 (PID.CoreNeed)\\46.82 (PID.OutgroupInteraction)} &  & \makecell[l]{ 0.01 (PID.CoreNeed)\\40.96 (PID.OutgroupInteraction)} &  & \makecell[l]{0.02 (PID.CoreNeed)\\0.20 (PID.Competence)\\0.14 (PID.Autonomy)\\0.00 (PID.Relatedness)} &  & \makecell[l]{0.01 (PID.CoreNeed)\\0.00 (PID.Competence)\\0.00 (PID.Autonomy)\\0.00 (PID.Relatedness)} &  & \makecell[l]{0.05 (PID.CoreNeed)\\0.01 (PID.Competence)\\0.00 (PID.Autonomy)\\0.01 (PID.Relatedness)} & \\
\hspace{1em}$\rho_{01}$ & \makecell[c]{ 0.01 (PID.CoreNeed)\\-0.27 (PID.OutgroupInteraction)} &  & \makecell[c]{ 0.27 (PID.CoreNeed)\\-0.68 (PID.OutgroupInteraction)} &  & \makecell[c]{-0.15 (PID.CoreNeed)\\-0.68 (PID.OutgroupInteraction)} &  & \makecell[c]{ 0.55 (PID.CoreNeed)\\-0.15 (PID.Competence)\\-0.09 (PID.Autonomy)\\ 0.56 (PID.Relatedness)} &  & \makecell[c]{-0.16 (PID.CoreNeed)\\-0.05 (PID.Competence)\\-0.44 (PID.Autonomy)\\-0.20 (PID.Relatedness)} &  & \makecell[c]{-0.25 (PID.CoreNeed)\\-0.29 (PID.Competence)\\-0.23 (PID.Autonomy)\\ 0.02 (PID.Relatedness)} & \\
\hspace{1em}$\rho_{00}$ & 0.33 (PID.CoreNeed-OutgroupInteraction) &  & -0.08 (PID.CoreNeed-OutgroupInteraction) &  & 0.01 (PID.CoreNeed-OutgroupInteraction) &  & \makecell[r]{ 0.03 (PID.CoreNeed-Autonomy)\\-0.93 (PID.Competence-Autonomy)\\-0.11 (PID.CoreNeed-Competence)\\ 0.17 (PID.CoreNeed-Relatedness)\\ 0.16 (PID.Competence-Relatedness)\\-0.10 (PID.Autonomy-Relatedness)} &  & \makecell[r]{ 0.60 (PID.CoreNeed-Autonomy)\\ 0.83 (PID.Competence-Autonomy)\\ 0.20 (PID.CoreNeed-Competence)\\ 0.42 (PID.CoreNeed-Relatedness)\\-0.79 (PID.Competence-Relatedness)\\-0.35 (PID.Autonomy-Relatedness)} &  & \makecell[r]{ 0.57 (PID.CoreNeed-Autonomy)\\-0.68 (PID.Competence-Autonomy)\\ 0.09 (PID.CoreNeed-Competence)\\-0.27 (PID.CoreNeed-Relatedness)\\-0.31 (PID.Competence-Relatedness)\\-0.08 (PID.Autonomy-Relatedness)} & \\

### 2021-12-16 Tables/mdlTheory.tex
linebreaks

\hspace{1em}$\tau_{11}$ &  &  & 0.05 (PID.CoreNeed) &  & 0.05 (PID.CoreNeed)\n0.04 (PID.Quality) &  & 0.12 (PID.CoreNeed) &  & 0.02 (PID.CoreNeed) &  & 0.00 (PID.CoreNeed)\n0.04 (PID.Quality) &  & 0.09 (PID.CoreNeed) &  & 0.05 (PID.CoreNeed) &  & 0.03 (PID.CoreNeed)\n0.02 (PID.Quality) &  & 0.11 (PID.Allport) &  & 0.05 (PID.Allport) &  & 0.02 (PID.Allport)\n0.02 (PID.Quality) &  & 0.00 (PID.CoreNeed)\n0.04 (PID.Allport) & \\
\hspace{1em}$\rho_{01}$ &  &  & 0.03 (objVar$cor.slope_intercept.) &  & 0.37 (PID.CoreNeed)\n-0.22 (PID.Quality) &  & -0.09 (objVar$cor.slope_intercept.) &  & -0.16 (objVar$cor.slope_intercept.) &  & -0.18 (PID.CoreNeed)\n-0.06 (PID.Quality) &  & -0.26 (objVar$cor.slope_intercept.) &  & -0.26 (objVar$cor.slope_intercept.) &  & -0.14 (PID.CoreNeed)\n-0.41 (PID.Quality) &  & -0.07 (objVar$cor.slope_intercept.) &  & -0.19 (objVar$cor.slope_intercept.) &  & 0.12 (PID.Allport)\n-0.51 (PID.Quality) &  & -1.00 (PID.CoreNeed)\n-0.07 (PID.Allport) & \\

>>>>

\hspace{1em}$\tau_{11}$ &  &  & 0.05 (PID.CoreNeed) &  & \makecell[l]{0.05 (PID.CoreNeed)\\0.04 (PID.Quality)} &  & 0.12 (PID.CoreNeed) &  & 0.02 (PID.CoreNeed) &  & \makecell[l]{0.00 (PID.CoreNeed)\\0.04 (PID.Quality)} &  & 0.09 (PID.CoreNeed) &  & 0.05 (PID.CoreNeed) &  & \makecell[l]{0.03 (PID.CoreNeed)\\0.02 (PID.Quality)} &  & 0.11 (PID.Allport) &  & 0.05 (PID.Allport) &  & \makecell[l]{0.02 (PID.Allport)\\0.02 (PID.Quality)} &  & \makecell[l]{0.00 (PID.CoreNeed)\\0.04 (PID.Allport)} & \\
\hspace{1em}$\rho_{01}$ &  &  & 0.03 (objVar$cor.slope_intercept.) &  & \makecell[c]{ 0.37 (PID.CoreNeed)\\-0.22 (PID.Quality)} &  & -0.09 (objVar$cor.slope_intercept.) &  & -0.16 (objVar$cor.slope_intercept.) &  & \makecell[c]{-0.18 (PID.CoreNeed)\\-0.06 (PID.Quality)} &  & -0.26 (objVar$cor.slope_intercept.) &  & -0.26 (objVar$cor.slope_intercept.) &  & \makecell[c]{-0.14 (PID.CoreNeed)\\-0.41 (PID.Quality)} &  & -0.07 (objVar$cor.slope_intercept.) &  & -0.19 (objVar$cor.slope_intercept.) &  & \makecell[c]{ 0.12 (PID.Allport)\\-0.51 (PID.Quality)} &  & \makecell[c]{-1.00 (PID.CoreNeed)\\-0.07 (PID.Allport)} & \\
